---
title: "STAT 184 Final Project" 
author: "Zhongqi Zhang"
date: Dec 10, 2019
output: html_notebook
---

```{r}
# clean up workspace environment
rm(list = ls())
# get packages installed
library(DataComputing)
# load my data set
setwd("~/Downloads")
car = read.table("car_data.csv",sep = ",",header = T)
car
```

## Research Question

**Which factor would have greater effect on mpg? Body style or make?**

```{r}
car %>% 
  group_by(body_style) %>%
  summarise(city_mpg = mean(city_mpg)) %>%
  arrange(desc(city_mpg))
```

**We see that the body style with highest city mpg is "hatchback".**

```{r}
car %>% 
  group_by(make) %>%
  summarise(city_mpg = mean(city_mpg)) %>%
  arrange(desc(city_mpg))
```

**We see that the make with highest city mpg is called "chevrolet", especially the body style "hatchback" and "sedan".**

```{r}
ggplot(data=car,aes(x=X,y=city_mpg))+geom_point()+aes(colour=make)+facet_wrap(~body_style,ncol=2) 
```

**In these plots, since color(stands for make) distributes quite similarly in each plot(stands for body style), we can get the conclusion that body style is not a main factor of mpg, because at least we cannot observe a very obvious difference from different body style. Therefore, I would draw the conclusion that make would have greater influence on mpg than body style does.**
